ISSP Chile 1999, 2009 & 2019 - Salary Gap & meritocracy

### 2019-07-02 files/20190622_ISSP1999_2009_2019-Chilejuitsa.Rmd
update 2 de julio

m1per99 <- '
gah_nmerit=~wfami+knope+corru
recom=~refor+rinte
'
fit1 <- cfa(model = m1per99,data = merit99)
summary(fit1, fit.measures=TRUE, standardized=TRUE)
```

>>>>

m1per99 <- '
gah_nmerit=~wfami+knope+corru
recom=~refor+rinte
'
fit1 <- cfa(model = m1per99,data = merit99)

```{r Tabla: CFA, results='asis'}
semTable::semTable(fit1, columns = c("estse", "p"),
                     fits = c("chisq","cfi", "rmsea"),type = "html") 
```

```{r plot CFA 1}
semPlot::semPaths(fit1, "std", 
                  edge.color = "black", 
                  style = "ram", 
                  exoVar = TRUE, 
                  intercepts = F,
                  thresholds = F,
                  fade =F)
```
